### 2019-03-22 Rapport/TG_ITA/Bibliographic_analysis/Coursera.tex
First coding of communication system
And notes chapter 1 book intro to comm systems

Analytic solution (faster convergence)
	The value of $ \theta = (X^{T}X)^{-1}X^{T}y $ (normal equation) gives the optimal value of $\theta$ that minimizes $ J(\theta) $
	Don't need to iterate nor choose $\alpha$.
	Compute the inverse costs a lot $\mathcal{O}(n^{3})$. So it is preferably to use if n is small over the iterative method.
	Noninvertibility: pinv -> pseudo inverse: calculates the value of the inverse even if it is non inversible.

>>>>

Analytic solution (faster convergence)
	The value of $ \theta = (X^{T}X)^{-1}X^{T}y $ (normal equation) gives the optimal value of $\theta$ that minimizes $ J(\theta) $ and doesn't need feature scaling.
	Don't need to iterate nor choose $\alpha$.
	Compute the inverse costs a lot $\mathcal{O}(n^{3})$. So it is preferably to use if n is small over the iterative method.
	Noninvertibility: pinv -> pseudo inverse: calculates the value of the inverse even if it is non inversible.
